### 2015-10-01 os-class/A2/writeup.tex
Change structure of directory. Make it a repository for all my school stuff: classes, resume, etc...

\section{Questions}
Point of assignment: To get us used to the level of difficulty of programming assignments, to give an introduction to system programming and file IO. To show how complicated even simple Linux tools are. \\
Correctness testing: By running the ar command and checking for exact duplication of behavior. Also by checking to see if output from myar could be run with ar and vice versa. I ran most of my tests with simple 3-character .txt files. The program works with more complicated text files; I can't imagine it working differently for larger files than 3-character ones. \\
Learn: I learned next time I need to start earlier. Also I learned lots about IO and string manipulation.\\

>>>>

\section{Questions}
\textbf{Point of assignment}: To get us used to the level of difficulty of programming assignments, to give an introduction to system programming and file IO. To show how complicated even simple Linux tools are. \\ \\
\textbf{Correctness testing}: By running the ar command and checking for exact duplication of behavior. Also by checking to see if output from myar could be run with ar and vice versa. I ran most of my tests with simple 3-character .txt files. The program works with more complicated text files; I can't imagine it working differently for larger files than 3-character ones. \\ \\
\textbf{Learn}: I learned next time I need to start earlier. Also I learned lots about IO and string manipulation.\\ \\
